### 2025-05-23 sec/authoring-workflow.tex

\subsection{Editor Loop}\label{subsec:editor-loop}
Design of main loop that would be integrated into an IDE. The configuration (state) that is being maintained
is a \kw{Paragraph} the user is authoring in Fluid. Consists of a sequence of text fragments, some of which
are uninterpreted (plain literals), the remainder have underlying expressions linking the text to raw or derived
data.

@@

\subsection{Paragraph with generated expression}
Figure \ref{fig:fluid-example-paragraph} shows the Fluid code of a Paragraph with Fluid expression generated by the authoring assistant.
Figure \ref{fig:fluid-scigen} shows the Fluid code written for the scigen datasets and examples.
\begin{figure}[h]
    \small
    {\lstinputlisting[language=Fluid]{website/authoring-assistant/fluid/1805.02474v1-10.fld}}
    \vspace{-0.5em}
    \caption{Fluid source code example Paragraph}
    \label{fig:fluid-example-paragraph}
\end{figure}

>>>>

\subsection{Editor Loop}
\label{subsec:editor-loop}
Design of main loop that would be integrated into an IDE. The configuration (state) that is being maintained
is a \kw{Paragraph} the user is authoring in Fluid. Consists of a sequence of text fragments, some of which
are uninterpreted (plain literals), the remainder have underlying expressions linking the text to raw or derived
data.

@@

\subsection{Loopback System}
\label{subsec:loopback-system}

Once the Authoring Assistant has generated the expression, it is executed by the Fluid interpreter.
If execution fails, the error is sent back to the LLM for regeneration.
This \textit{loopback} mechanism enables iterative refinement of expressions, improving accuracy and robustness.
Three types of errors are handled:

\begin{itemize}
    \item \textbf{Interpreter Error}.
    Syntax errors due to incorrect use of the language (e.g., undeclared functions, invalid syntax, etc.).
    \item \textbf{String Error}.
    The expression does not return a string, violating the requirements of the \textit{System Prompt} (Fig.~\ref{fig:system-prompt}).
    \item \textbf{Value Mismatch}.
    If an expected value is known, it is compared with the actual result.
    The mismatch generates an error.
\end{itemize}

\subsection{Paragraph with generated expression}
\label{subsec:paragraph-with-generated-expression}
Figure \ref{fig:fluid-example-paragraph} shows the Fluid code of a Paragraph with Fluid expression generated by the authoring assistant.
Figure \ref{fig:fluid-scigen} shows the Fluid code written for the scigen datasets and examples.
\begin{figure}[h]
    \small
    {\lstinputlisting[language=Fluid]{website/authoring-assistant/fluid/1805.02474v1-10.fld}}
    \vspace{-0.5em}
    \caption{Fluid source code example Paragraph}
    \label{fig:fluid-example-paragraph}
\end{figure}
